Syntax Is All You Need: A Universal-Language Approach to Mutant Generation

### 2023-03-30 paper/main.tex
fix typo and small edit

\begin{table}[htbp]
\centering
\caption{Java (Our Implementation vs. PIT vs. LittleDarwin).
  Determining it PIT bytecode mutants are equivalent is extremely
  difficult to do with reasonable accuracy, so we did not attempt it.  LittleDarwin produces no equivalent mutants.}
\label{tab:table_java2}
\resizebox{\columnwidth}{!}{% again don't love it, but footnotesize is actually smaller than necessary
\begin{tabular}{l|rrr|rr|rr}
\toprule
                 & \mc{3}{c|}{\textbf{Comby}}   & \mc{2}{c|}{\textbf{PIT}} & \mc{2}{c}{\textbf{LittleDarwin}} \\
\textbf{Project} & \textbf{Muts.} &  \makecell{\textbf{Mut.} \\ \textbf{Score}} & \textbf{\% Eqv}
& \textbf{Muts.} &  \makecell{\textbf{Mut.} \\ \textbf{Score}}
& \textbf{Muts.} &  \makecell{\textbf{Mut.} \\ \textbf{Score}} \\ \midrule

@@

Finally, for Rust, we observed that the Cargo-Mutants tool simply does
not generate many mutants.  Mutation scores were broadly similar to
ours, though lower, and none of the generated mutants we examined were
equivalent, but for one project Cargo-Mutants did not produce
\emph{any} mutants even though our tool was able to produce a large
number of non-equivalent unkilled mutants.  Our tool did produce a
very large percentage of equivalent mutants for one project, and high
percentage for another project, but these numbers are still well
within the range of expected results in past inspections of
equivalent mutants.  We also note  that for Rust the cost for invalid
mutants is unusually low, due to the availability of {\tt cargo check}
which very quickly checks that code compiles, without actually
compiling it, making our approach more attractive.  Some C++ compilers
also offer fast syntax check facilities, e.g., {\tt -fsyntax-only} in g++.

>>>>

\begin{table}[htbp]
\centering
\caption{Java (Our Implementation vs. PIT vs. LittleDarwin).
  Determining if PIT bytecode mutants are equivalent is extremely
  difficult to do with reasonable accuracy, so we did not attempt it.  LittleDarwin produces no equivalent mutants.}
\label{tab:table_java2}
\resizebox{\columnwidth}{!}{% again don't love it, but footnotesize is actually smaller than necessary
\begin{tabular}{l|rrr|rr|rr}
\toprule
                 & \mc{3}{c|}{\textbf{Comby}}   & \mc{2}{c|}{\textbf{PIT}} & \mc{2}{c}{\textbf{LittleDarwin}} \\
\textbf{Project} & \textbf{Muts.} &  \makecell{\textbf{Mut.} \\ \textbf{Score}} & \textbf{\% Eqv}
& \textbf{Muts.} &  \makecell{\textbf{Mut.} \\ \textbf{Score}}
& \textbf{Muts.} &  \makecell{\textbf{Mut.} \\ \textbf{Score}} \\ \midrule

@@

Finally, for Rust, we observed that the Cargo-Mutants tool simply does
not generate many mutants for a particular source file.  Mutation scores were broadly similar to
ours, though lower, and none of the generated mutants we examined were
equivalent, but for one project Cargo-Mutants did not produce
\emph{any compilable} mutants even though our tool was able to produce a large
number of non-equivalent unkilled mutants.  Our tool did produce a
very large percentage of equivalent mutants for one project, and high
percentage for another project, but these numbers are still well
within the range of expected results in past inspections of
equivalent mutants.  We also note  that for Rust the cost for invalid
mutants is unusually low, due to the availability of {\tt cargo check}
which very quickly checks that code compiles, without actually
compiling it, making our approach more attractive.  Some C++ compilers
also offer fast syntax check facilities, e.g., {\tt -fsyntax-only} in g++.
